\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2015-03-25 doc/sw-system.tex
Up to section 4 working through AV comments #96

For the more interesting subjects, the CI offers two features that  enable
further investigation of the subjects. The first is the ``Quick Dashboard'' (QD)
a more advanced image viewer. This allows the viewer to compare three different
contrast and color balance settings, to help bring out subtle features, and to
pan and zoom in on interesting regions of the image to assess small features.
Markers can be placed in the Quick Dashboard just the same as in the main CI
image viewer. The second is a link to that subject's page in the project
discussion forum, \texttt{http://talk.spacewarps.org} (known as ``Talk''). Here,
volunteers can discuss the features they have seen either before they submit
their classification, or after, if they ``favorite'' the subject. There is no
``back'' button: each volunteer may only classify a given subject once. However,
the presence of an option to see what others think about any given subject
before submitting your own classification means that the classifications may not
be strictly independent; the advantage of this system is that volunteers can
learn from others what constitutes a good lens candidate. This is not, however,
the primary educational resource; we describe the explicit training that we
provide for the volunteers in the next section.

@@

% PJM IS HERE

@@

The CFHT Legacy Survey \citep[CFHTLS,][]{CFHTLS} covered XXX square degrees of
approximately equatorial sky, in four patches distributed in right ascension,
over the course of N years. With homegeneous image quality of, typically, X
arcsec (in the $i$-band), and reaching limiting magnitudes of XX-XX in the
$ugriz$ filter set, this survey has yielded several dozen new gravitational
lenses on both galaxy and group scales \citep{}. The quality of the data,
combined with the presence of these comparison ``known lens'' samples, made
this a natural choice against which to develop and test the \sw system. The
CFHTLS is also well-representative of the data quality expected from several
next-generation sky surveys, such as DES, KiDS, HSC and LSST.

In order to investigate the completeness of the previous, semi-automated, lens
searches in the CFHTLS area, we designed a ``blind search.'' We divided the
mosaiced images into some 430,000 equal size, overlapping tiles, approximately
70~arcsec on a side. Each of these images is a ``test image'' (as opposed to a
``training image''). In future, larger area projects we expect to implement
the rather different strategy of producing image tiles centred on particular
pre-selected ``targets,'' to make for a more efficient (but less complete)
survey. We do not expect the performance of citizen image inspectors to change
significantly between these strategies: to first order, both strategies
require the inspectors to learn what lenses look like, and then search the
presented images for similar features.

@@

The CFHTLS $g$, $r$ and $i$-band images have the greatest depth and best image
quality, and we chose to focus on this set (although the $u$ and $z$-band
images were also available for inspection in Talk). We made colour composite
images using publically-available code\footnote{The open source  colour image
composition code used in this work is available from
\texttt{http://github.com/drphilmarshall/HumVI}} following the prescription of
\citet{LuptonEtal}. Specifically, we first rescaled the pixel values of each
channel image into flux units, and then applied an arcsinh stretch. The
stretch parameters were chosen using a small random sample of images, to
ensure that the background noise was just visible,  and that the centres of
bright, intermediate resdhift galaxies were not saturated. The color scales
were chosen to maximize the contrast between faint extended objects. These
parameters were then fixed during the production of all the tiles, in order to
allow straightforward comparison between one image and another, and for
intuition to be built up about the appearance of stars and galaxies across the
survey. Alternative algorithms, such as adjusting the stretch and scale
dynamically according to, for example, the root-mean-square pixel value in
each image, can lead to better presentation of bright objects, but in doing so
they tend to hide the faint features in those images: we needed to optimize
the detectability of these faint features.   Examples of CFHTLS training set
images can be seen in \Fref{fig:training-gallery:duds} and
\Fref{fig:training-gallery:sims}.

>>>>

For the more interesting subjects, the CI offers two features that  enable
further investigation of the subjects. The first is the ``Quick Dashboard'' (QD)
a more advanced image viewer. This allows the viewer to compare three different
contrast and colour balance settings, to help bring out subtle features, and to
pan and zoom in on interesting regions of the image to assess small features.
Markers can be placed in the Quick Dashboard just the same as in the main CI
image viewer. The second is a link to that subject's page in the project
discussion forum, \texttt{http://talk.spacewarps.org} (known as ``Talk''). Here,
volunteers can discuss the features they have seen either before they submit
their classification, or after, if they ``favorite'' the subject. There is no
``back'' button: each volunteer may only classify a given subject once. However,
the presence of an option to see what others think about any given subject
before submitting your own classification means that the classifications may not
be strictly independent; the advantage of this system is that volunteers can
learn from others what constitutes a good lens candidate. This is not, however,
the primary educational resource; we describe the explicit training that we
provide for the volunteers in the next section. The FITS images of the subject can be further explored with Zooniverse ``Dashboard Tools,'' using a more powerful image viewer that enables dynamic variation of the colour balance and contrast (stretch), and for any given view to be shared via unique URL back to Talk.

@@

@@

The CFHT Legacy Survey \citep[CFHTLS,][]{CFHTLS} covered 171 square degrees of
approximately equatorial sky, in four patches distributed in right ascension.
With high and homogeneous image quality (the mean seeing in the $g$-band is
0.78''), and reaching limiting magnitudes of around 25 across the $ugriz$ filter
set, this survey has yielded several dozen new gravitational lenses on both
galaxy and group scales
\citep{GavazziEtal2014,SonnenfeldEtal13,CabanacEtal2007,MoreEtal2012}. The
quality of the data, combined with the presence of these comparison ``known
lens'' samples, makes this a natural choice against which to develop and test
the \sw system. The CFHTLS is also well-representative of the data quality
expected from several next-generation sky surveys, such as DES, KiDS, HSC and
LSST.

In order to investigate the completeness of the previous, semi-automated, lens
searches in the CFHTLS area, we designed a ``blind search.'' We divided the
mosaiced images into some 430,000 equal size, overlapping tiles, approximately
70~arcsec on a side. We refer to these images as ``test images'' (as opposed to
``training images''). In future, larger area projects we expect to implement the
rather different strategy of producing image tiles centred on particular
pre-selected ``targets,'' to make for a more efficient (but less complete)
survey. We do not expect the performance of citizen image inspectors to change
significantly between these strategies: to first order, both strategies require
the inspectors to learn what lenses look like, and then search the presented
images for similar features.

@@

The CFHTLS $g$, $r$ and $i$-band images have the greatest depth and best image
quality, and we chose to focus on this set (although the $u$ and $z$-band images
were also available for perusal in Talk). We made colour composite PNG format
images\footnote{The open source colour image composition code used in this work
is available from \texttt{http://github.com/drphilmarshall/HumVI}} following the
prescription of \citet{LuptonEtal2004} \citep[with extensions
by]{WherryEtal2004}. Specifically, we first rescaled the pixel values of each
channel image into flux units, and then applied an arcsinh stretch. The stretch
parameters were optimized by visually inspecting a small randomly-selected
sample of images, to ensure that the background noise was just visible,  and
that the centres of bright, intermediate redshift galaxies were not saturated.
The color scales were chosen to maximize the contrast between faint extended
objects. These parameters were then fixed during the production of all the
tiles, in order to allow straightforward comparison between one image and
another, and for intuition to be built up about the appearance of stars and
galaxies across the survey. Alternative algorithms, such as adjusting the
stretch and scale dynamically according to, for example, the root-mean-square
pixel value in each image, can lead to better presentation of bright objects,
but in doing so they tend to hide the faint features in those images: we needed
to optimize the detectability of these faint features.   Examples of CFHTLS
training set images prepared in this way can be seen in the galleries of the
previous section (Figures~\ref{fig:training-gallery:sims}
and~\ref{fig:training-gallery:duds}). We also defined two alternative sets of visualization parameters, to display a ``bluer'' image and a ``brighter'' image in the classification interface Quick Dashboard (\Sref{sec:design:interface}). The QD code performs the same image composition as just described, but dynamically on FITS images in the browser. These FITS images are also available for viewing in Talk, via the main Zooniverse Dashboard image display tool, which again offers the same stretch settings, as a starting point for image exploration.

% PJM IS HERE.
